\documentclass{letter}
\usepackage{hyperref}
\signature{Henrik Qvigstad}
\address{
  Henrik Qvigstad\\
  \href{mailto:henrik.qvigstad@gmail.com}{henrik.qvigstad@gmail.com}\\
  +47 97606794
}

\begin{document}

\begin{letter}{reMarkable AS}
  \opening{To the hiring team,}

  I am writing to express my sincere interest in the Senior Software Engineer
  position at reMarkable, as recently advertised on LinkedIn. I  am excited
  about
  the opportunity to contribute my skills and expertise to reMarkable.

  With previous positions at Dignio Kindly, Kantega, and Opera, I have a
  proven track record of over 8 years of experience in web application
  development.	I also hold an M.Sc.\ in Physics from the University of Bergen.
  In addition the the education, I have 5 years of experience in academic work.

  In my current role as a Senior Software Developer at Dignio, I have served
  as a tech lead and architect for their web application rewrite.
  This experience has honed my abilities in leadership, architecting innovative
  solutions,
  and collaborating effectively with cross-functional teams, skills that I
  believe will be valuable at reMarkable.

  Although my professional experience is mostly in development and in
  front-end, I do have some backend experience, doing fairly non-trivial work,
  that I would be happy to elaborate on in an interview.

  I also have some experience with C++ development from my time at Opera and
  academic work. In my education, I have also completed an introductory
  class in C++ programming that included basic Qt development. I know that this
  might not be a particularly strong  C++ background, but I would love to have
  the opportunity to contribute to your C++ codebase as well.

  I am impressed by reMarkable's mission to help people think better in a
  distracted world and the company's commitment to fostering a collaborative
  and
  supportive work environment. I believe that my experience and qualifications
  will make me an excellent addition to reMarkable.

  Thank you for considering my application. I look forward to hearing from you.

  \closing{Best regards,}
\end{letter}
\end{document}
